Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-27 docs/_tex/index.tex
add results

@@

@@

>>>>

To assess the impact of spatial resolution on the model's output, the
reflectance of each flight's orthomosaic was spatially resampled using
the average method from the Terra package in R. DISCOV was then applied
to these resampled rasters. The results were compared to the original
model predictions, which were resampled using the mode method from the
Terra package in R. For each resolution and each class of the model, an
agreement percentage was obtained, where a score of 100 indicates that
all pixels in the two products are identical, and a score of 0 indicates
that all pixels are different.

We used a Generalized Linear Model (GLM) with a Gaussian family and an
identity link function to investigate the relationship between pixel
resolution, vegetation class, and their interaction on the response
variable, the agreement. The formula for the model was:

\begin{equation}\phantomsection\label{eq-gam}{
Agreement \sim  Resolution \times VegetationClass
}\end{equation}

@@

Figure~\ref{fig-pixelsize} shows an effect of the pixel size on the
agreement between the two products. The highest resolution in which the
resampling has been performed is 10 cm. At this resolution, the
agreement has already decreased from 78\% (red algae) to 94\%
(seagrass), depending on the class. As pixel size increases, the
agreement between the products declines steadily for all classes. This
decline is most pronounced for green algae, which experiences the
sharpest drop in agreement as pixel size increases beyond 10 m, reaching
below 0\% at a pixel size of 30 m. Seagrass maintain higher levels of
agreement at coarser resolutions, although a clear decline is still
observed, with seagrasses dropping from over 94\% at 10 cm to around
88\% at 30 m. Brown algae and red algae show a more moderate decline
compared to red algae, with agreement levels remaining around 62\% and
40\%, respectively, at 30 m resolution.

@@

The Generalized Linear Model (GLM) analysis revealed a significant
effect of pixel resolution on the agreement, with a negative
relationship (\[\beta = -1.0334 \times 10^{-8}, p < 0.001\]). This
indicates that as pixel resolution increases, the proportion of the
response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement.
Magnoliopsida showed a significant positive effect
(\[\beta = 0.1202, p < 0.001\]), suggesting that this class was
associated with a higher agreement.
